### 2022-03-11 ch1.tex
finish contributions and future directions

\section{Contributions and Future Directions}
\begin{center}
    \texttt{UNDERGOING CHANGES}
\end{center}

% TODO make Broader Impact more relevant to actual findings
% Original

This research will first and foremost impact sociology. While the spread
of information is investigated in the discipline (diffusion, mass
communication, social influence), it is almost always from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This perspective aligns with Uses and
Gratifications Theory, discussed in Section B: Background, and sees
people as active agents in their search for information instead of just
passive receivers of information signals.

Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find; the information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.

Additionally, this dissertation will investigate how social norms are
formed in situations of uncertainty, an area that is less developed in
sociology. While sociologists have studied social norms since the
formation of the discipline, focus on the quick formation of social
norms has implications for social behavioral outcomes, cultural change,
organizational reactions to unrest and disasters, and many more areas
that influence humanity.

This dissertation will also have implications for the study of social
networks and social support. Not only is this work situated in the
sociological study of social support and social influence, but I utilize
rarely-used-in-sociology sources of big data to better understand these
mechanisms and test existing theories.

This dissertation also contributes to computational social science \&
critical big data studies. I base much of my dissertation around Google
Search Trends, which are relatively underutilized in the social sciences
compared to health sciences and business. Not only does this project
introduce Google Search Trends in new ways, but I perform explicit tests
of how this data should be used in the social sciences, providing the
groundwork for this exciting source of big data for future computational
social scientists. Because my research takes a critical big data studies
approach, I take into account the potential pitfalls with any source of
big data (McFarland and McFarland 2015) and attempt to explicitly answer
questions posed by this field, such as "what are the behavioral
processes that lead to macro-level outcomes" proposed by \citet{breigerScaling2015}.

I also make important contributions to social epidemiology through this
research. Each of the three papers in this dissertation use health case
studies for questions of sociological interest. Because of this, I will
contribute to social epidemiological questions on vaccine hesitancy,
health communication, and diffusion of high-risk health behaviors. While
all of these areas are important to social epidemiology, there are
potential important health implications for these contributions on
outside of the academy.

Outside of the academic research impacts that this dissertation makes,
there are clear and timely social implications that will stem from this
work. First, by uncovering how norms are created during norm
uncertainty, I may be able to establish recommendations for
interventions to be applied during disasters and other times of unrest
to promote effective positive norms. Second, my research may have
implications for how to optimize gratifications in search processes to
promote healthy social relationships and improved online algorithm
deployment.

This work also relates to polarization and misinformation, two major
social issues of our time. \citet{axelrodDisseminationCultureModel1997} shows that network structure,
autocorrelation, and diffusion create local convergence of attitudes and
culture which then leads to global polarization \citep{dellapostaWhyLiberalsDrink2015}. In investigating how local diffusion leads to social norms
through information search, some of my findings may have strong
implications and interventions for the prevention of global
polarization. Relatedly, understanding where and how people search for
information has implications for the information they are exposed to and
the norms they develop. This project will attempt to relate to where
misinformation is uncovered and how to intervene in its absorption.

>>>>

\section{Contributions and Future Directions}

% search as an agentic process
This research will make contributions to multiple subfields and literatures. 
First and foremost, these articles make a contribution to the sociological literature.
The spread of information has long been investigated in the discipline (diffusion, mass
communication, social influence). However, it is almost always researched from a structural
perspective which disregards individual agency and choice in the
acquisition of new information. This dissertation adopts the second perspective,
centering people as active agents in their search for information algined
with their own preferences and gratifications instead of just
passive receivers of information signals.
Taking this agentic perspective is critical in the study of information
diffusion when combined with cognitive perspectives like that of
Goldberg and Stein (2018). How people search for information determines
the information that they find. The information they uncover is filtered
through cognitive biases and predispositions to how they interpret and
act upon the newfound information. Searching for informational support
through social network ties theoretically will uncover potentially
different information than that would be uncovered through online web
search and will change how people are organized and how people behave.
\hyperlink{paper-2}{Article 2} importantly shows that 
the vehicles uses to search for information have a significant impact on the choice to get vaccinated against Covid-19, a real-world consequence to the minutiae of individual information search.

% CSS & big data
This dissertation also contributes to computational social science \&
critical big data studies. I base much of my dissertation around Google
Search Trends, which are relatively underutilized in the social sciences
compared to health sciences and business. Because \hyperlink{paper-1}{Article 1} 
takes a critical big data studies approach, I take into account the potential
pitfalls with any source of big data \citep{mcfarlandBigDataDanger2015} and explicitly
test just how well Google Trends can be used as an indicator for different concepts. 
Importantly, I find that there is no replacement for high quality survey data with Google Trends. 
This is a large contribution to the field of critical big data studies but also provides
the groundwork for future tests of external validity for big data for future computational
social scientists.

% micro behaviors to macro processes
Bridging the contribution of search as an agentic process 
and critical big data studies, this dissertation contributes to the question posed by 
\citet{breigerScaling2015}, "what are the behavioral processes that 
lead to macro-level outcomes?" With the exponentially growing size of digital-trace data
that is available, it is important to not only uncover the external validity of 
the data and correspondence to real world behaviors (see \hyperlink{paper-1}{Article 1})
but also important to understand the social forces that leads to the big data. 
One of the contributions of \hyperlink{paper-2}{Article 2} dives deep
into this question, uncovering why some people choose to use web search engines over other
information-vehicles. These papers are a first step in validating and establishing
a deeper understanding of who the users are that contribute to macro-level aggregate trends.

% social norms
Additionally, this dissertation investigates how social norms are
formed in situations of uncertainty, an area that is far less developed in
sociology. While sociologists have studied social norms since the
formation of the discipline, norms are most often studied under the lens
of the emergence of norms and transmission of norms between groups, 
deviance and social control, the interaction of norms as "mental representations of appropriate behavior" \citep{aarts2003silence}, and research categorizing different types of norms (e.g. descriptive versus injunctive, prescriptive versus proscriptive).  
The focus on the formation of new social norms during times of upheaval 
has implications for interventions in social behavioral outcomes, 
research on cultural change, and the spread of cognitive associations. 
Moreover, \hyperlink{paper-3}{Article 3} focuses on how how conflicting
behaviors become settled into cognitive associations, providing
a relevant framework for research on unrest and disasters.

% social networks / diffusion
This dissertation will also have implications for the study of social
networks and diffusion. \citet{centolaComplexContagionsWeakness2007}
introduced a pivotal disruption to the diffusion literature when
they developed complex contagion, the need for reinforcement through multiple
exposures.  \hyperlink{paper-3}{Article 3} in this dissertation
takes this disruption one step further to demonstrate that the concordance
of the exposure affects the contagion process; in other words, being exposed to a 
diversity of diffusants (discordance) can prevent the diffusant from spreading. 
This critical finding provides many fields of exploration for scholars 
to further the interdependence between different beliefs that are diffusing and
under what contexts the discordance matters.

% social epidemiology
I also make important contributions to social epidemiology through this
research. Each of the three papers in this dissertation use health case
studies for questions of sociological interest. Because of this, I 
contribute to the social epidemiological conversation on vaccine hesitancy,
health communication, and diffusion of high-risk health behaviors. While
all of these areas are important to social epidemiology, there hold
potential important health implications for these contributions on
outside of the academy, covered in the first paragraphs of this chapter.

%  polarization misinformation
% This work also relates to polarization and misinformation, two major
% social issues of our time. \citet{axelrodDisseminationCultureModel1997} shows that network structure,
% autocorrelation, and diffusion create local convergence of attitudes and
% culture which then leads to global polarization \citep{dellapostaWhyLiberalsDrink2015}. In investigating how local diffusion leads to social norms
% through information search, some of my findings may have strong
% implications and interventions for the prevention of global
% polarization. Relatedly, understanding where and how people search for
% information has implications for the information they are exposed to and
% the norms they develop. This project will attempt to relate to where
% misinformation is uncovered and how to intervene in its absorption.
